Outstanding Title

### 2017-04-19 writing/EpiDraft.Rmd
Add changes for script for pulling data

>>>>

```{r}
library(rvest)
library(purrr)
library(dplyr)
library(stringr)
library(lubridate)
library(tidyr)
library(ggplot2)

## For 2017

i <- str_pad(1:14, pad = "0", width = 2)
url <- i %>% map(~paste("https://wonder.cdc.gov/mmwr/mmwr_2017.asp?mmwr_year=2017&mmwr_week=", as.character(.x), "&mmwr_table=2J&request=Submit&mmwr_location=", sep=""))
html_2017 <- url %>% map(~read_html(.x))

week_end_date <- html_2017 %>% 
  map(~html_nodes(.x, 'tr:nth-child(1) td:nth-child(1)')) %>% 
  map(~html_text(.x)) %>% 
  map(~ str_extract(.x[1], "week ending .+ \\(")) %>% 
  map(~ str_replace(.x[1], "week ending", "")) %>% 
  map(~ str_replace(.x[1], "\\(", "")) %>% 
  map(~ str_trim(.x[1]))

nodes_midatlantic <- html_2017 %>% map(~html_nodes(.x, 'tr:nth-child(12) td:nth-child(2)'))
madat <- nodes_midatlantic %>% map(~html_text(.x))
as.numeric(madat)

nodes_nyc <- html_2017 %>% map(~html_nodes(.x, 'tr:nth-child(15) td:nth-child(2)'))
nycdat <- nodes_nyc %>% map(~html_text(.x))
as.numeric(nycdat)

nodes_pa <- html_2017 %>% map(~html_nodes(.x, 'tr:nth-child(16) td:nth-child(2)'))
padat <- nodes_pa %>% map(~html_text(.x))
as.numeric(padat)

leg_cases_2017 <- data_frame(week_end_date = as.character(week_end_date),
                        midatlantic = as.numeric(madat),
                        nyc = as.numeric(nycdat),
                        penn = as.numeric(padat)) %>% 
  mutate(week_end_date = mdy(week_end_date))

## For 2016

i <- str_pad(1:52, pad = "0", width = 2)
url <- i %>% map(~paste("https://wonder.cdc.gov/mmwr/mmwr_2016.asp?mmwr_year=2016&mmwr_week=", as.character(.x), "&mmwr_table=2G&request=Submit&mmwr_location=", sep=""))
html_2016 <- url %>% map(~read_html(.x))

week_end_date <- html_2016 %>% 
  map(~html_nodes(.x, 'tr:nth-child(1) td:nth-child(1)')) %>% 
  map(~html_text(.x)) %>% 
  map(~ str_extract(.x[1], "week ending .+ \\(")) %>% 
  map(~ str_replace(.x[1], "week ending", "")) %>% 
  map(~ str_replace(.x[1], "\\(", "")) %>% 
  map(~ str_trim(.x[1]))

nodes_midatlantic <- html_2016 %>% map(~html_nodes(.x, 'tr:nth-child(13) td:nth-child(12)'))
madat <- nodes_midatlantic %>% map(~html_text(.x))
as.numeric(madat)

nodes_nyc <- html_2016 %>% map(~html_nodes(.x, 'tr:nth-child(16) td:nth-child(12)'))
nycdat <- nodes_nyc %>% map(~html_text(.x))
as.numeric(nycdat)

nodes_pa <- html_2016 %>% map(~html_nodes(.x, 'tr:nth-child(17) td:nth-child(12)'))
padat <- nodes_pa %>% map(~html_text(.x))
as.numeric(padat)

leg_cases_2016 <- data_frame(week_end_date = as.character(week_end_date),
                        midatlantic = as.numeric(madat),
                        nyc = as.numeric(nycdat),
                        penn = as.numeric(padat)) %>% 
  mutate(week_end_date = mdy(week_end_date))

## For 2015

i <- str_pad(1:52, pad = "0", width = 2)
url <- i %>% map(~paste("https://wonder.cdc.gov/mmwr/mmwr_2015.asp?mmwr_year=2015&mmwr_week=", as.character(.x), "&mmwr_table=2G&request=Submit&mmwr_location=", sep=""))
html_2015 <- url %>% map(~read_html(.x))

week_end_date <- html_2015 %>% 
  map(~html_nodes(.x, 'tr:nth-child(1) td:nth-child(1)')) %>% 
  map(~html_text(.x)) %>% 
  map(~ str_extract(.x[1], "week ending .+ \\(")) %>% 
  map(~ str_replace(.x[1], "week ending", "")) %>% 
  map(~ str_replace(.x[1], "\\(", "")) %>% 
  map(~ str_trim(.x[1]))

nodes_midatlantic <- html_2015 %>% map(~html_nodes(.x, 'tr:nth-child(13) td:nth-child(12)'))
madat <- nodes_midatlantic %>% map(~html_text(.x))
as.numeric(madat)

nodes_nyc <- html_2015 %>% map(~html_nodes(.x, 'tr:nth-child(16) td:nth-child(12)'))
nycdat <- nodes_nyc %>% map(~html_text(.x))
as.numeric(nycdat)

nodes_pa <- html_2015 %>% map(~html_nodes(.x, 'tr:nth-child(17) td:nth-child(12)'))
padat <- nodes_pa %>% map(~html_text(.x))
as.numeric(padat)

leg_cases_2015 <- data_frame(week_end_date = as.character(week_end_date),
                             midatlantic = as.numeric(madat),
                             nyc = as.numeric(nycdat),
                             penn = as.numeric(padat)) %>% 
  mutate(week_end_date = mdy(week_end_date))

# Putting two years together

leg_cases <- bind_rows(leg_cases_2015, leg_cases_2016, leg_cases_2017)

leg_cases %>% 
  gather(key = location, value = cases, - week_end_date) %>% 
  ggplot(aes(x = week_end_date, y = cases, color = location)) + 
  #geom_point() + 
  geom_line() + 
  theme_classic() + 
  theme(legend.position = "top")
```
